---
title: "linear model from Web"
author: "Tracy Alset"
date: " summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS
### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```

It looks like there is an obvious linear relationship between SIMS and ARM, meaning as arm length increases the better the performance of the worker in the simulation is . 


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point()
```



### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation coefficient is somewhat close to 1 showing a decent linear relationship between SIMS and ARM. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

Based on the inferential results, looking at the adjusted r squared value and the residual standard error, it looks like this model is linear till a certain extend. the error isn't that high so it shows that the data that we have in this model doesn't really differ from the actual data.


#### Predict at target point

```{r}
TargetARM<- data.frame(ARM=88 , Grip=94)
```

```{r}
predict(model.1, TargetARM,interval ="prediction")
```


#### scatterplot with model fit
  
```{r}
basicNN + geom_point()+ geom_lm()
```  
  
  95% of the points above and below the best fit line are within 2*residual standard error. 
  

## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
plot(SIMS~GRIP,data=data)
```

the scatter plot shows somewhat a descent linear relationship between SIMS and GRIP.



### Numerical results 


```{r}
cor(SIMS~GRIP,data=data)
```

The correlation coefficient is somewhat close to 1 showing a decent linear relationship between SIMS and GRIP.

### Inferential  (Build model.2)
  



#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

